---
title: "Final Project - Phase 1"
author: "Colby Fry"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries and importing dataset
```{r, Load Libraries & Datasets}
library(tidyverse)
library(mice)
library(VIM)
library(UpSetR)
library(naniar)
library(tidymodels)
library(glmnet)
library(rpart)
library(rpart.plot)
library(rattle)
library(caret)

train_csv <- read_csv("train.csv")

```
## Factor Conversions in the Train Dataset
```{r Factor Conversion & Cleaning}
train_csv <- train_csv %>%
  mutate(attribute_0 = as_factor(attribute_0)) %>%
  mutate(attribute_1 = as_factor(attribute_1)) %>%
  mutate(attribute_2 = as_factor(attribute_2)) %>%
  mutate(attribute_2 = fct_recode(attribute_2, "material_5" = "5", "material_8" = "8", "material_6" = "6", "material_9" = "9")) %>%
  mutate(attribute_3 = as_factor(attribute_3)) %>%
  mutate(attribute_3 = fct_recode(attribute_3, "material_5" = "5", "material_8" = "8", "material_6" = "6", "material_9" = "9")) %>%
  mutate(product_code = as_factor(product_code)) %>%
  mutate(failure = as_factor(failure)) %>%
  mutate(failure = fct_recode(failure, "0" = "No", "1" = "Yes")) 

summary(train_csv)

```

## Visualizing Missingness

```{r Missingness Visualization}
gg_miss_var(train_csv)
```

## Outlier detection

```{r}
ggplot(train_csv, aes(x=loading)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_0)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_1)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_2)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_3)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_4)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_5)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_6)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_7)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_8)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_9)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_10)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_11)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_12)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_13)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_14)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_15)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_16)) + geom_histogram()

ggplot(train_csv, aes(x=measurement_17)) + geom_histogram()

```


## Imputation of new data into Train

```{r Imputation using mice, into train}
set.seed(123456)
impu_measures <- mice(train_csv, m = 5, method = 'pmm', printFlag = FALSE)
summary(impu_measures)
```
## Sample density plot post-imputation, using the "loading" variable

```{r Visualize Before & After - Imputations, using loading as an example}
densityplot(impu_measures, ~loading)
```

## Merging the newly imputed data into the original Train dataset
### Summary Statistics
```{r Merging imputed values with the original dataset}
train_new <- complete(impu_measures)
summary(train_new)
```
## Categorical Variable Distribution Visualizations

```{r Categorical Dist Viz}
ggplot(train_new, aes(x = product_code, fill = factor(failure))) + 
  geom_bar(position = "fill") + 
  theme_minimal() + 
  labs(title = "product_code by Failure Status")

ggplot(train_new, aes(x = attribute_0, fill = factor(failure))) + 
  geom_bar(position = "fill") + 
  theme_minimal() + 
  labs(title = "attribute_0 by Failure Status")

ggplot(train_new, aes(x = attribute_1, fill = factor(failure))) + 
  geom_bar(position = "fill") + 
  theme_minimal() + 
  labs(title = "attribute_1 by Failure Status")

ggplot(train_new, aes(x = attribute_2, fill = factor(failure))) + 
  geom_bar(position = "fill") + 
  theme_minimal() + 
  labs(title = "attribute_2 by Failure Status")

ggplot(train_new, aes(x = attribute_3, fill = factor(failure))) + 
  geom_bar(position = "fill") + 
  theme_minimal() + 
  labs(title = "attribute_3 by Failure Status")
```



## Numerical Variable Distribution Visualizations


```{r Visualizing Distribution of Numerical Variables}
ggplot(train_new, aes(x = factor(failure), y = loading, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_0, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_1, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_2, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_3, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_4, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_5, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_6, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_7, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_8, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_9, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_10, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_11, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_12, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_13, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_14, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")


ggplot(train_new, aes(x = factor(failure), y = measurement_15, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "loading by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_16, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")

ggplot(train_new, aes(x = factor(failure), y = measurement_17, fill = factor(failure))) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "measurement_8 by Failure Status")
```

#Modeling

## Logistic Regression

```{r}
set.seed(123) 
train_split = initial_split(train_new, prop = 0.70, strata = failure)
train = training(train_split)
test = testing(train_split)
```

### Numerical Relationships - Train Split
```{r}
ggplot(train,aes(x=failure, y=loading)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_0)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_1)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_2)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_3)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_4)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_5)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_6)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_7)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_8)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_9)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_10)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_11)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_12)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_13)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_14)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_15)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_16)) + geom_boxplot() + 
  theme_bw()

ggplot(train,aes(x=failure, y=measurement_17)) + geom_boxplot() + 
  theme_bw()
```

## First Logistic Regression Model
```{r}
traincsv_model = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm")

traincsv_recipe = recipe(failure ~., train)

logreg_wf = workflow() %>%
  add_recipe(traincsv_recipe) %>% 
  add_model(traincsv_model)

traincsv_fit = fit(logreg_wf, train)

options(scipen = 999)
summary(traincsv_fit$fit$fit$fit)
options(scipen = 0)
```

